\ttitle

### 2013-12-13 Chapters/Chapter3/one_class_classification.tex
Fix typos

Boundary methods are based on Vapnik's principle\footnote{With a limited amount of data available, on should avoid solving a more general problem as an intermediate step to solve the original problem \cite{vapnik1998statistical}.} which imply in this case that estimating the complete data density for a \gls{occ} may be too complex, in case one is only interested in the closed boundary.
Examples of methods that focus on the boundary (a direct threshold) of the training data distribution are K-centers, Nearest-neighborhood and \gls{svdd} or a combination of those methods \cite{hempstalk2008one}.
Especially the latter has a strong bias towards minimal volume solutions.
These type of methods are sensitive to scaling of features, since they rely on a well-defined distance measure.
The number of objects that is required is smaller than in the case of density methods.
The boundary method \gls{svdd}, constructed by Tax and which has shown good performance \cite{khan2010survey}, will be further discussed in \Cref{subsec:oc-svm-svdd}.

>>>>

Boundary methods are based on Vapnik's principle\footnote{With a limited amount of data available, one should avoid solving a more general problem as an intermediate step to solve the original problem \cite{vapnik1998statistical}.} which imply in this case that estimating the complete data density for a \gls{occ} may be too complex, in case one is only interested in the closed boundary.
Examples of methods that focus on the boundary (a direct threshold) of the training data distribution are K-centers, Nearest-neighborhood and \gls{svdd} or a combination of those methods \cite{hempstalk2008one}.
Especially the latter has a strong bias towards minimal volume solutions.
These type of methods are sensitive to scaling of features, since they rely on a well-defined distance measure.
The number of objects that is required is smaller than in the case of density methods.
The boundary method \gls{svdd}, constructed by Tax and which has shown good performance \cite{khan2010survey}, will be further discussed in \Cref{subsec:oc-svm-svdd}.

### 2013-12-13 Chapters/Chapter3/one_class_svm.tex
Fix typos

\begin{figure}
\centering
  \includegraphics[width=0.8\textwidth]{./Figures/chapter3/svm_kernel_mapping.png}
  \caption[Kernel mapping]{The non-linear boundary in the input space $\mathcal{I}$ (left) is transformed to a linear boundary in the feature space $\mathcal{F}$ (right) by mapping the data points with the function $\phi$. The kernel trick uses a function $K$ which performs an implicit mapping. Image from Wikipedia.org\footnotemark}
  \label{fig:kernel_mapping}
\end{figure}
\footnotetext{\url{http://en.wikipedia.org/wiki/File:Kernel_Machine.png}}

@@

The constructed hypersphere is characterized by a center $\mathbf{a}$ and a radius $R > 0$ as distance from the center to (any data point that is a \gls{sv} on) the boundary, for which the volume, and thus the radius $R$, will be minimized.
The center $\mathbf{a}$ is a linear combination of of the support vectors.
Like the classical \gls{svm} and \gls{svdd} it can be required that all the distances from the data points $x_i$ to the center $\mathbf{a}$ are strict less then $R$ (or equivalent measure, to create a hard margin) or soft margins are allowed by using slack variables $\xi_i$.
In the case of a soft margin, the penalty is determined by $C$ and the minimization is expressed as \Cref{eq:svdd_objective}.
This principle is illustrated in the right image or \Cref{fig:nu-vs-svdd}.
Instead of a separating hyperplane, constructed by \gls{nu-svm} and illustrated on the left of the Figure, the \gls{svdd} creates a hypersphere (in the illustration a cricle) around the data points.
By using kernel functions (\eg the \gls{rbf}) the hyperspheres in the high dimensional feature space $\mathcal{F}$ corresponds to a flexible and tight enclosing boundary in input space $\mathcal{I}$.
Possible resulting closed boundaries are illustrated in \Cref{fig:svdd-boundary}.
This enclosing boundary is obtained by minimizing the following error function $L$ which contains the volume of the hypersphere and the distance from the boundary to the outlier objects:
\begin{equation}\label{eq:svdd_objective}
  L(R, \vectorsym{a}, \vectorsym{\xi}) = R^2 + C \sum_{i=1}^n \xi_i
\end{equation}
\begin{equation}
  \begin{multlined}
    \mbox{ subject to: } \\
    \begin{aligned}
      \lVert x_i - \mathbf{a} \rVert ^ 2 \leq & R^2 + \xi_i & \mbox{ for all } i = 1, \dots, n \\
      & \xi_i \geq 0 & \mbox{ for all } i = 1, \dots, n \\
    \end{aligned}
  \end{multlined}
\end{equation}
In the dual Lagrangian formulation of this error function $L$ the multipliers $\vectorsym{\alpha}$ are maximized:
\begin{equation}\label{eq:svdd_lagrange}
  L = \sum_{i} \alpha_i(x_i \cdot x_i) - \sum_{i,j} \alpha_i \alpha_j(x_i \cdot x_j)
\end{equation}
\begin{equation}
  \begin{multlined}
    \mbox{ subject to: } \\
    \begin{aligned}
    0 \le \alpha_i \le C, \sum_{i} \alpha_i = 1
    \end{aligned}
  \end{multlined}
\end{equation}

>>>>

\begin{figure}
\centering
  \includegraphics[width=0.8\textwidth]{./Figures/chapter3/svm_kernel_mapping.png}
  \caption[Kernel mapping]{The non-linear boundary in the input space $\mathcal{I}$ (left) is transformed to a linear boundary in the feature space $\mathcal{F}$ (right) by mapping the data points with the function $\phi$. The kernel trick uses a function $K$ which performs an implicit mapping. Image from Wikipedia.org}
  \label{fig:kernel_mapping}
\end{figure}

@@

The constructed hypersphere is characterized by a center $\mathbf{a}$ and a radius $R > 0$ as distance from the center to (any data point that is a \gls{sv} on) the boundary, for which the volume, and thus the radius $R$, will be minimized.
The center $\mathbf{a}$ is a linear combination of of the support vectors.
Like the classical \gls{svm} and \gls{svdd} it can be required that all the distances from the data points $x_i$ to the center $\mathbf{a}$ are strict less than $R$ (or equivalent measure, to create a hard margin) or soft margins are allowed by using slack variables $\xi_i$.
In the case of a soft margin, the penalty is determined by $C$ and the minimization is expressed as \Cref{eq:svdd_objective}.
This principle is illustrated in the right image or \Cref{fig:nu-vs-svdd}.
Instead of a separating hyperplane, constructed by \gls{nu-svm} and illustrated on the left of the Figure, the \gls{svdd} creates a hypersphere (in the illustration a cricle) around the data points.
By using kernel functions (\eg the \gls{rbf}) the hyperspheres in the high dimensional feature space $\mathcal{F}$ corresponds to a flexible and tight enclosing boundary in input space $\mathcal{I}$.
Possible resulting closed boundaries are illustrated in \Cref{fig:svdd-boundary}.
This enclosing boundary is obtained by minimizing the following error function $L$ which contains the volume of the hypersphere and the distance from the boundary to the outlier objects:
\begin{equation}\label{eq:svdd_objective}
  L(R, \vectorsym{a}, \vectorsym{\xi}) = R^2 + C \sum_{i=1}^n \xi_i
\end{equation}
\begin{equation}
  \begin{multlined}
    \mbox{ subject to: } \\
    \begin{aligned}
      \lVert x_i - \mathbf{a} \rVert ^ 2 \leq & R^2 + \xi_i & \mbox{ for all } i = 1, \dots, n \\
      & \xi_i \geq 0 & \mbox{ for all } i = 1, \dots, n \\
    \end{aligned}
  \end{multlined}
\end{equation}
In the dual Lagrangian formulation of this error function $L$ the multipliers $\vectorsym{\alpha}$ are maximized:
\begin{equation}\label{eq:svdd_lagrange}
  L = \sum_{i} \alpha_i(x_i \cdot x_i) - \sum_{i,j} \alpha_i \alpha_j(x_i \cdot x_j)
\end{equation}
\begin{equation}
  \begin{multlined}
    \mbox{ subject to: } \\
    \begin{aligned}
    0 \le \alpha_i \le C, \sum_{i} \alpha_i = 1
    \end{aligned}
  \end{multlined}
\end{equation}
